Marshall and Olkin-G and Gamma-G family of distribution: properties and applications

### 2022-05-18 paper/paper.tex
Update paper

\documentclass[twoside,leqno,11pt]{article}
\usepackage{revstat-v2}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{color}

@@

\vspace{1.5cm}
\title{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications
	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
}
\renewcommand{\titleheading}
{Using the ``revstat-v2.sty" Package}  % --- on odd running heads

\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
	{Department of Statistics,
		Federal University of Pernambuco,\\
        Pernambuco, Recife, Brazil
		\ (maria@de.ufpe.br)}
	\\
	\authoraddress{Gauss M. Cordeiro \href{https://orcid.org/0000-0002-3052-6551}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
	{Department of Statistics,
		Federal University of Pernambuco,\\
		Pernambuco, Recife, Brazil
		\ (gauss@de.ufpe.br)}
	\\
	\authoraddress{Pedro Rafael D. Marinho \href{https://orcid.org/0000-0003-1591-8300}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
	\correspondingauthor}
	{Department of Statistics,
		Federal University of Paraíba,\\
		Paraíba, João Pessoa, Brazil
		\ (pedro.rafael.marinho@gmail.com)}
}
\renewcommand{\authorheading}
{Author Pedro Rafael D. Marinho}  % --- on even running heads

@@

%-------------------------------------------------------------------------------
% AMS classifications...
%-------------------------------------------------------------------------------
\begin{ams}
	49A05, 78B26.
\end{ams}

\section{Introduction}

@@

\section{The New Family}\label{sec:MOGaG}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale =  0.39]{pdf-hazard.pdf}
\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
\end{center}
\end{figure}

@@

\section{Estimation}\label{estimation}

@@

\section{Simulations}\label{sec:simulation}

@@

\section{Applications}\label{applications}

@@

\section{Mathematical properties}\label{properties}

@@

\section{Conclusions}\label{conclusions}

@@

\appendix

\section{Appendix: Simulation code}\label{ap:simulation}

The script below is used to perform the simulations whose results are given in Table \ref{tab:bias} of Section \ref{sec:simulation}.
It is developed a script using the programming language {\sf R} to be used in other simulations or even to check the results presented in this paper.

\section*{References}

\begin{description}

@@

\end{description}

>>>>

\documentclass[twoside,leqno,11pt]{article}
\usepackage{revstat-v2}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{color}
\usepackage{caption}
\usepackage{subcaption}

@@

\vspace{1.5cm}
\title{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications
	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
}
\renewcommand{\titleheading}
{MOGG family of distribution: properties and applications}  % --- on odd running heads

\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
	{Department of Statistics,
		Federal University of Pernambuco,\\
        Pernambuco, Recife, Brazil
		\ (maria@de.ufpe.br)}
	\\
	\authoraddress{Gauss M. Cordeiro \href{https://orcid.org/0000-0002-3052-6551}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
	{Department of Statistics,
		Federal University of Pernambuco,\\
		Pernambuco, Recife, Brazil
		\ (gauss@de.ufpe.br)}
	\\
	\authoraddress{Pedro Rafael D. Marinho \href{https://orcid.org/0000-0003-1591-8300}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
	\correspondingauthor}
	{Department of Statistics,
		Federal University of Paraíba,\\
		Paraíba, João Pessoa, Brazil
		\ (pedro.rafael.marinho@gmail.com)}
}
\renewcommand{\authorheading}
{Maria do Carmo S. Lima, Gauss M. Cordeiro and Pedro Rafael D. Marinho, }  % --- on even running heads

@@

%-------------------------------------------------------------------------------
% AMS classifications...
%-------------------------------------------------------------------------------
\begin{ams}
	60E05, 62E10, 62E15.
\end{ams}

\section{INTRODUCTION}

@@

\section{THE NEW FAMILY}\label{sec:MOGaG}

@@

%\begin{figure}[H]
%\begin{center}
%\includegraphics[scale =  0.39]{pdf-hazard.pdf}
%\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
%\end{center}
%\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{pdf_function.pdf}
		\caption{MO-$\Gamma$-W density function.}
		\label{fig:pdf}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{hazard_function.pdf}
		\caption{MO-$\Gamma$-W hazard function.}
		\label{fig:hazard}
	\end{subfigure}
\caption{MO-$\Gamma$-W density function and  MO-$\Gamma$-W hazard function with G following the Weibull distribution.}
\label{formas}
\end{figure}

@@

\section{ESTIMATION}\label{estimation}

@@

\section{SIMULATIONS}\label{sec:simulation}

@@

\section{APPLICATIONS}\label{applications}

@@

\section{MATHEMATICAL PROPERTIES}\label{properties}

@@

\section{CONCLUSIONS}\label{conclusions}

@@

\begin{thebibliography}{8}

@@

\end{thebibliography}
